Predicting Sakura Florescence in Japan with a Dual-Model Approach

### 2024-11-18 paper/Paper.qmd
Update Paper and reference (second draft)
This is the second draft of this paper. References are now complete. Paper contents are now all complete. Further change will be uploaded as third draft.

---
title: ""
subtitle: ""
author: 
  - Shaotong (Max) Li
thanks: "Code and data are available at: [Sakura_Florescence_Prediction](https://github.com/ShaotongLi-Max/Sakura_Florescence_Prediction.git)."
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false

#### Workspace setup ####

@@

# Data

@@

@@

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Combine and Prepare Data ####
# Prepare sakura_historical_cleaned data
historical_flower_data <- sakura_historical_cleaned %>%
  select(flower_doy) %>%
  filter(!is.na(flower_doy)) %>%  # Remove missing values
  mutate(dataset = "Historical")  # Add label for distinction

@@

#### Plot Flowering Day Distribution ####
flower_doy_distribution_plot <- combined_flower_data %>%
  ggplot(aes(x = flower_doy, fill = dataset, color = dataset)) +
  geom_density(alpha = 0.3, adjust = 1.5) +  # Use density plot for smoother curves
  labs(
    title = "Flowering Day Distribution: Historical vs Modern Data",
    x = "Flowering Day (DOY)",
    y = "Density",
    fill = "Dataset",
    color = "Dataset"
  ) +
  scale_fill_manual(values = c("Historical" = "steelblue", "Modern" = "darkorange")) +
  scale_color_manual(values = c("Historical" = "steelblue", "Modern" = "darkorange")) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.position = "right"
  )

@@

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Combine and Prepare Data ####
# Prepare sakura_historical_cleaned data
historical_temp_data <- sakura_historical_cleaned %>%
  select(temp) %>%
  filter(!is.na(temp)) %>%  # Remove missing values
  mutate(dataset = "Historical", variable = "temp")  # Add labels for distinction

@@

#### Plot Temperature Distribution ####
temp_distribution_plot <- combined_temp_data %>%
  ggplot(aes(x = temp, fill = dataset, color = dataset)) +
  geom_density(alpha = 0.3, adjust = 1.5) +  # Use density plot for smoother curves
  labs(
    title = "Temperature Distribution: Historical vs Modern Data",
    x = "Temperature (°C)",
    y = "Density",
    fill = "Dataset",
    color = "Dataset"
  ) +
  scale_fill_manual(values = c("Historical" = "steelblue", "Modern" = "darkorange")) +
  scale_color_manual(values = c("Historical" = "steelblue", "Modern" = "darkorange")) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.position = "right"
  )

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Prepare Data ####
# sakura_historical is already loaded
scatter_data <- sakura_historical_cleaned %>%
  filter(!is.na(temp), !is.na(flower_doy))  # Ensure no missing values

#### Create Scatter Plot ####
scatter_plot_no_line <- ggplot(scatter_data, aes(x = temp, y = flower_doy)) +
  geom_point(aes(color = year), alpha = 0.6, size = 2) +  # Scatter points colored by year
  scale_color_viridis_c(option = "C", name = "Year") +  # Color scale for year
  labs(
    title = "Relationship Between Temperature and Flowering Day",
    subtitle = "Color represents temporal progression",
    x = "Temperature (°C)",
    y = "Flowering Day (DOY)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )

@@

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Improved Plot Latitude and Longitude Distributions ####

# Plot latitude distribution with bins
latitude_plot <- ggplot(sakura_modern_cleaned, aes(x = latitude)) +
  geom_histogram(
    bins = 20,                    # Adjust the number of bins for better grouping
    fill = "steelblue", 
    alpha = 0.8
  ) +
  labs(
    title = "Latitude Distribution",
    x = "Latitude",
    y = "Count"
  ) +
  theme_minimal()

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Prepare Latitude Data ####
latitude_temp_data <- sakura_modern_cleaned %>%
  filter(!is.na(latitude), !is.na(mean_temp_month)) %>%
  group_by(latitude) %>%
  summarise(mean_temp = mean(mean_temp_month, na.rm = TRUE)) %>%
  ungroup()

@@

#### Create Plot ####
latitude_temp_plot <- ggplot(latitude_temp_data, aes(x = latitude, y = mean_temp)) +
  geom_line(color = "steelblue", size = 1) +  # Line graph with custom color and size
  geom_abline(
    slope = coef(linear_model)["latitude"],
    intercept = coef(linear_model)["(Intercept)"],
    color = "darkorange",
    linetype = "dashed",
    size = 1
  ) +  # Add a dashed line for the linear relationship
  labs(
    title = "Mean Temperature by Latitude",
    subtitle = "Relationship between Latitude and Mean Temperature with Linear Trend",
    x = "Latitude",
    y = "Mean Temperature (°C)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )

@@

```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Load and Prepare Data ####
# Calculate mean temperature for each location
temperature_summary <- sakura_modern_cleaned %>%
  group_by(latitude, longitude) %>%
  summarise(mean_temp_month = mean(mean_temp_month, na.rm = TRUE)) %>%
  ungroup()

@@

#### Create the Map for Temperature ####
gis_plot_temp <- ggplot(data = japan_map) +
  geom_sf(fill = "white", color = "black") +  # Base map of Japan
  geom_point(
    data = temperature_summary,
    aes(x = longitude, y = latitude, color = mean_temp_month),
    size = 3, alpha = 0.7
  ) +
  scale_color_gradientn(
    colors = c("#2c7bb6", "#abd9e9", "#ffffbf", "#fdae61", "#d7191c"),  # Blue to red gradient
    name = "Mean Temperature (°C)"
  ) +
  theme_minimal() +
  labs(
    title = "Average Monthly Temperatures Across Japan",
    subtitle = "Warmer colors indicate higher temperatures",
    x = "Longitude",
    y = "Latitude"
  ) +
  theme(legend.position = "right")

@@

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Plot Monthly Distribution of Flower Date ####

@@

# Plot the monthly distribution
flower_month_plot <- ggplot(flower_month_distribution, aes(x = month, y = n)) +
  geom_bar(stat = "identity", fill = "steelblue", alpha = 0.8) +  # Use steelblue for the bars
  labs(
    title = "Monthly Distribution of Flower Date",
    x = "Month",
    y = "Count"
  ) +
  theme_minimal()

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Plot Distribution of Flower Dates by Month and Day ####

@@

# Plot the line graph
flower_date_line_plot <- ggplot(flower_date_summary, aes(x = day, y = count, color = month, group = month)) +
  geom_line(size = 1) +  # Draw smooth lines for each month
  scale_color_manual(values = color_palette) +  # Use a color palette for all months
  labs(
    title = "Flower Date Distribution by Month and Day",
    x = "Day of the Month",
    y = "Count",
    color = "Month"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right"
  )

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Plot Distribution of Temperature by Date ####

@@

# Create the plot
temperature_plot <- ggplot(temperature_distribution, aes(x = day_of_year, y = mean_temp_month)) +
  geom_point(alpha = 0.5, color = "steelblue") +  # Scatter plot of temperature
  geom_smooth(method = "loess", color = "darkorange", size = 1, se = FALSE) +  # Smoothed line for trend
  labs(
    title = "Temperature Distribution by Date",
    subtitle = "Scatter plot with temperature trend over the year",
    x = "Day of the Year",
    y = "Temperature (°C)"
  ) +
  scale_x_continuous(
    breaks = c(1, 32, 60, 91, 121, 152),  # Manually specify breaks for Jan, Feb, Mar, Apr, May
    labels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun")  # Correct labels
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Load and Prepare Data ####
# Calculate mean flower_doy for each location
sakura_summary <- sakura_modern_cleaned %>%
  group_by(latitude, longitude) %>%
  summarise(mean_flower_doy = mean(flower_doy, na.rm = TRUE)) %>%
  ungroup()

@@

#### Create the Map ####
gis_plot <- ggplot(data = japan_map) +
  geom_sf(fill = "white", color = "black") +  # Base map of Japan
  geom_point(
    data = sakura_summary,
    aes(x = longitude, y = latitude, color = mean_flower_doy),
    size = 3, alpha = 0.7
  ) +
  scale_color_viridis_c(
    option = "D",  # Viridis color scale for better visualization
    name = "Mean Flower DOY"
  ) +
  theme_minimal() +
  labs(
    title = "Average Flowering Dates Across Japan",
    subtitle = "Darker points indicate later flowering dates",
    x = "Longitude",
    y = "Latitude"
  ) +
  theme(legend.position = "right")

# Display the plot
print(gis_plot)
```
## Excluded Variables

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Prepare Data ####
# sakura_historical_cleaned is already loaded
line_data <- sakura_historical_cleaned %>%
  filter(!is.na(temp), !is.na(year))  # Ensure no missing values

@@

#### Create Line Plot ####
line_plot <- ggplot(line_data, aes(x = year, y = temp)) +
  geom_line(color = "steelblue", size = 1) +  # Line graph with color and size
  geom_hline(
    yintercept = mean_temp, 
    color = "darkorange", 
    linetype = "dashed", 
    size = 1
  ) +  # Add horizontal dashed line for reference
  labs(
    title = "Temperature Trend Over Years",
    subtitle = "Yearly average temperature with reference line",
    x = "Year",
    y = "Temperature (°C)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )

@@

@@

```
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#### Prepare Longitude Data ####
longitude_temp_data <- sakura_modern_cleaned %>%
  filter(!is.na(longitude), !is.na(mean_temp_month)) %>%
  group_by(longitude) %>%
  summarise(mean_temp = mean(mean_temp_month, na.rm = TRUE)) %>%
  ungroup()

>>>>

---
title: "Predicting Sakura Florescence in Japan with a Dual-Model Approach"
subtitle: "Estimating Temperature and Forecasting Bloom Duration for Cherry Blossoms"
author: 
  - Shaotong (Max) Li
thanks: "Code and data are available at: [Sakura_Florescence_Prediction](https://github.com/ShaotongLi-Max/Sakura_Florescence_Prediction.git)."
date: 2024/11/17
date-format: long
abstract: "This paper presents a dual-model approach to predict the duration of cherry blossom blooms in Japan: The first model predicts bloom duration using temperature, while the second model estimates temperature based on latitude, month, and date. By analyzing historical and modern data, we provide insights into how latitude and seasonal timing affect temperature and bloom duration. Our findings indicate that this dual-model approach enhances our understanding of climatic effects on cherry blossom florescence, highlighting potential impacts of climate change on one of Japan's most cherished natural events."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false

#### Workspace setup ####
install.packages("tidyverse")
install.packages("arrow")
install.packages("here")
install.packages("ggplot2")
install.packages("patchwork")
install.packages("tidyverse")
install.packages("sf")
install.packages("rnaturalearth")
install.packages("rnaturalearthdata")
install.packages("ggthemes")
install.packages("dplyr")
install.packages("knitr")
install.packages("kableExtra")

@@

Cherry blossoms, or sakura, are a powerful symbol of Japan, representing both the fleeting beauty of nature and a cherished cultural heritage [@Wikipedia2024]. Each spring, the blooming of cherry blossoms is celebrated across the country, marking a time of renewal and festivity [@Wikipedia2024]. However, the timing and duration of these blooms are highly sensitive to climatic conditions, which makes predicting sakura florescence increasingly important in the face of climate change [@Ocko2024]. Understanding how environmental factors, such as temperature, latitude, and seasonal timing, influence bloom duration can help forecast these events and provide insight into broader ecological changes [@Ocko2024].

This paper aims to address the challenge of predicting cherry blossom bloom duration by using a dual-model approach. The first model predicts the duration of cherry blossom blooms using temperature. The second model estimates temperature based on environmental variables such as latitude, month, and date, providing a detailed understanding of local climatic conditions. By combining these two models, we seek to fill the gap in understanding how temperature fluctuations driven by geographic and temporal factors affect sakura florescence.

The estimand in this study is the predicted duration of cherry blossom (sakura florescence). Specifically, Model 1 predicts the duration of the bloom using temperature, while Model 2 estimates temperature as a function of latitude, month, and date. This dual-model structure allows us to precisely quantify the effect of temperature as a mediating factor influenced by geographical and temporal variables on bloom duration. This approach allows us to quantify the relationship between environmental conditions and the duration of cherry blossom blooms.

We utilized both historical and modern phenological data to ensure the robustness of our predictions. Our analysis highlights how latitude and seasonal factors contribute to temperature variation, which in turn affects the timing and duration of the bloom. The results demonstrate the potential for these models to improve the accuracy of bloom forecasts, particularly in the context of changing climatic patterns. This research contributes valuable knowledge to the fields of phenology and climate science, and provides practical implications for tourism, cultural events, and ecological conservation in Japan.

The remainder of this paper is structured as follows: @sec-data discusses the data sources and preprocessing methods. @sec-model details the dual-model approach, including the temperature estimation and bloom prediction models. @sec-result presents the results, followed by a discussion in @sec-discussion on the implications of our findings. Finally, @sec-appendix concludes with insights into future research directions and the broader impact of climate change on cherry blossoms.

# Data {#sec-data}

In this project, we used R[@citeR] and several R packages for data processing, analysis, and visualization. Specifically, tidyverse [@tidyverse], arrow[@arrow], here[@here], ggplot2[@ggplot2], patchwork[@patchwork], sf[@sf], rnaturalearth[@rnaturalearth], and rnaturalearthdata[@rnaturalearthdata] were used for data processing, geospatial analysis, and visualization. ggthemes[@ggthemes] was utilized to apply thematic elements to plots, while dplyr[@dplyr] was key for data manipulation tasks. For dynamic report generation, knitr[@knitr] and kableExtra[@kableExtra] were used, providing enhanced formatting for outputs. Together, these packages enabled efficient data cleaning, analysis, and visualization throughout the study.

@@

The data used in this study includes three primary datasets: historical cherry blossom bloom records, modern bloom records, and temperature data. The historical dataset  contains records of cherry blossom bloom dates across multiple decades for the Kyoto region, providing a long-term view of bloom trends in this specific area of Japan. The modern dataset  contains recent bloom dates from various regions across Japan, reflecting current climatic conditions and bloom dynamics. Lastly, the temperature dataset  includes temperature readings for various locations in Japan, which are essential for estimating temperature-related effects on bloom duration.

To ensure comparability, only bloom records that met our defined geographic and seasonal criteria were retained. This filtering process ensured that only reliable and relevant data points were used in the final analysis, thus maintaining the accuracy and robustness of our predictive models. Finally, the cleaned datasets were merged based on common identifiers such as location and time to create a comprehensive dataset for modeling sakura florescence.

The final combined dataset, after merging and filtering, consisted of 10,456 rows with multiple key attributes, including latitude, month, date, and temperature, serving as predictors for bloom duration. By integrating both historical and modern data, our analysis captures both long-term trends and recent shifts in bloom timing, providing insights into the effects of climate variability and change on cherry blossom phenology.

@@

The transformation of real-world phenomena into dataset entries involved detailed documentation of cherry blossom bloom dynamics. Historical sakura data was derived from records such as diary entries and observations from meteorological agencies, specifically focusing on the Kyoto region. Bloom dates were reconstructed based on these historical accounts dating back to 812 CE, supplemented by temperature data that provided context for climatic influences over centuries.

Modern cherry blossom data was collected by the Japan Meteorological Agency (JMA), including flowering dates and meteorological information across Japan since 1953. This dataset encompasses latitude, longitude, bloom dates, and temperature data, offering a comprehensive view of bloom dynamics under current climatic conditions. Temperature readings were matched with bloom records using geographic and temporal identifiers to ensure consistent analysis.

Data quality checks included removing incomplete records, standardizing date formats, and verifying bloom dates against multiple sources. This ensured that the final dataset was robust and suitable for modeling, enabling reliable predictions of bloom duration based on environmental factors.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-florescence
#| fig-cap: "Sakura Florescence: Historical vs Modern Data"

#### Combine and Prepare Data ####
# Prepare sakura_historical_cleaned data
historical_flower_data <- sakura_historical_cleaned %>%
  select(flower_doy) %>%
  filter(!is.na(flower_doy)) %>%  # Remove missing values
  mutate(dataset = "Historical")  # Add label for distinction

@@

#### Plot Flowering Day Distribution ####
flower_doy_distribution_plot <- combined_flower_data %>%
  ggplot(aes(x = flower_doy, fill = dataset, color = dataset)) +
  geom_density(alpha = 0.3, adjust = 1.5) +  # Use density plot for smoother curves
  labs(
    x = "Flowering Day (DOY)",
    y = "Density",
    fill = "Dataset",
    color = "Dataset"
  ) +
  scale_fill_manual(values = c("Historical" = "steelblue", "Modern" = "darkorange")) +
  scale_color_manual(values = c("Historical" = "steelblue", "Modern" = "darkorange")) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.position = "right"
  )

@@

```
The variable 'florescence' represents the duration of cherry blossom blooming, defined as the number of days during which cherry blossoms are in full bloom. In the historical dataset, which focuses on the Kyoto region, florescence data shows a narrower distribution, indicating relatively stable bloom timings over centuries. In contrast, the modern dataset includes bloom data from multiple regions across Japan, resulting in a wider distribution that reflects greater variability due to regional climatic differences.

@fig-florescence illustrates the density distribution of the day of year (DOY) for full bloom, comparing historical and modern datasets. The historical data (Kyoto) exhibits a peak around a consistent time frame, whereas the modern data shows more dispersed bloom times, likely driven by regional climatic variations and recent temperature changes.

As the outcome variable in our modeling approach, florescence is crucial for understanding bloom dynamics. It allows us to assess the impact of temperature and other environmental factors on the timing and length of cherry blossom blooms, providing insights into the effects of climate variability.

The distribution of florescence in the historical data shows relatively stable bloom timings, with less variability compared to the modern dataset. This stability is largely due to the consistent climatic conditions in the Kyoto region over centuries. In contrast, the modern data presents more pronounced regional variations in bloom duration, influenced by diverse environmental conditions across Japan. As the outcome variable in our modeling approach, florescence serves as the key measure of bloom dynamics, enabling us to evaluate how temperature and other environmental factors affect the timing and duration of cherry blossom blooms in both historical and modern contexts.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-temperature-1
#| fig-cap: "Temperature: Historical vs Modern Data"

#### Combine and Prepare Data ####
# Prepare sakura_historical_cleaned data
historical_temp_data <- sakura_historical_cleaned %>%
  select(temp) %>%
  filter(!is.na(temp)) %>%  # Remove missing values
  mutate(dataset = "Historical", variable = "temp")  # Add labels for distinction

@@

#### Plot Temperature Distribution ####
temp_distribution_plot <- combined_temp_data %>%
  ggplot(aes(x = temp, fill = dataset, color = dataset)) +
  geom_density(alpha = 0.3, adjust = 1.5) +  # Use density plot for smoother curves
  labs(
    x = "Temperature (°C)",
    y = "Density",
    fill = "Dataset",
    color = "Dataset"
  ) +
  scale_fill_manual(values = c("Historical" = "steelblue", "Modern" = "darkorange")) +
  scale_color_manual(values = c("Historical" = "steelblue", "Modern" = "darkorange")) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.position = "right"
  )

@@

Temperature plays a crucial role in determining the timing and duration of cherry blossom blooms. @fig-temperature-1 shows the density distribution of temperatures in historical and modern datasets, highlighting significant differences between the two periods. The historical dataset, primarily focused on the Kyoto region, shows a relatively narrow temperature range centered around moderate values, while the modern dataset presents a broader range with lower temperatures being more prevalent. This difference in temperature distributions likely reflects the increased regional variability and recent climatic changes observed in Japan.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-temperature-2
#| fig-cap: "Temperature VS Sakura Florescence"

#### Prepare Data ####
# sakura_historical is already loaded
scatter_data <- sakura_historical_cleaned %>%
  filter(!is.na(temp), !is.na(flower_doy))  # Ensure no missing values

#### Create Scatter Plot ####
scatter_plot_no_line <- ggplot(scatter_data, aes(x = temp, y = flower_doy)) +
  geom_point(aes(color = year), alpha = 0.6, size = 2) +  # Scatter points colored by year
  scale_color_viridis_c(option = "C", name = "Year") +  # Color scale for year
  labs(
    subtitle = "Color represents temporal progression",
    x = "Temperature (°C)",
    y = "Flowering Day (DOY)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right",
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )

@@

The strong linear relationship between temperature and the day of year (DOY) for full bloom is evident in @fig-temperature-2. As temperatures increase, the DOY for blooming decreases, indicating that higher temperatures lead to earlier blooming. This relationship is consistent across both historical and modern datasets, underscoring the critical impact of temperature on bloom timing. The temporal progression in @fig-temperature-2, represented by the color gradient, illustrates how this relationship has persisted over time, even as overall climatic conditions have changed.

In our modeling approach, temperature serves as a key predictor for florescence, allowing us to quantify how fluctuations in temperature directly affect the timing and duration of cherry blossom blooms. By examining the historical and modern temperature distributions, we can better understand the impacts of climate variability and identify trends that are crucial for predicting future bloom behavior.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-latitude-1
#| fig-cap: "Latitude Distribution"

#### Improved Plot Latitude and Longitude Distributions ####

# Plot latitude distribution with bins
latitude_plot <- ggplot(sakura_modern_cleaned, aes(x = latitude)) +
  geom_histogram(
    bins = 20,                    # Adjust the number of bins for better grouping
    fill = "steelblue", 
    alpha = 0.8
  ) +
  labs(
    x = "Latitude",
    y = "Count"
  ) +
  theme_minimal()

@@

@fig-latitude-1 shows the distribution of latitudes for the locations included in the dataset. The majority of observations are concentrated between latitudes 34° and 38° N, which represents the regions most commonly associated with cherry blossom observations in Japan. There is a smaller number of observations at lower and higher latitudes, reflecting the geographic range of sakura coverage in the country.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-latitude-2
#| fig-cap: "Latitude VS Temperature"

#### Prepare Latitude Data ####
latitude_temp_data <- sakura_modern_cleaned %>%
  filter(!is.na(latitude), !is.na(mean_temp_month)) %>%
  group_by(latitude) %>%
  summarise(mean_temp = mean(mean_temp_month, na.rm = TRUE)) %>%
  ungroup()

@@

#### Create Plot ####
latitude_temp_plot <- ggplot(latitude_temp_data, aes(x = latitude, y = mean_temp)) +
  geom_line(color = "steelblue", size = 1) +  # Line graph with custom color and size
  geom_abline(
    slope = coef(linear_model)["latitude"],
    intercept = coef(linear_model)["(Intercept)"],
    color = "darkorange",
    linetype = "dashed",
    size = 1
  ) +  # Add a dashed line for the linear relationship
  labs(
    subtitle = "Relationship with Linear Trend",
    x = "Latitude",
    y = "Mean Temperature (°C)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )

@@

@fig-latitude-2 illustrates the relationship between latitude and mean temperature, showing a clear positive trend. As latitude increases, so does the average temperature. The dashed orange line represents the linear trend, indicating a consistent increase in temperature as we move towards the northern regions of Japan. This relationship is essential for understanding how geographic position influences local climatic conditions, which in turn affects bloom timing.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-latitude-3
#| fig-cap: "Average Temperatures Across Japan"

#### Load and Prepare Data ####
# Calculate mean temperature for each location
temperature_summary <- sakura_modern_cleaned %>%
  group_by(latitude, longitude) %>%
  summarise(mean_temp_month = mean(mean_temp_month, na.rm = TRUE)) %>%
  ungroup()

@@

#### Create the Map for Temperature ####
gis_plot_temp <- ggplot(data = japan_map) +
  geom_sf(fill = "white", color = "black") +  # Base map of Japan
  geom_point(
    data = temperature_summary,
    aes(x = longitude, y = latitude, color = mean_temp_month),
    size = 3, alpha = 0.7
  ) +
  scale_color_gradientn(
    colors = c("#2c7bb6", "#abd9e9", "#ffffbf", "#fdae61", "#d7191c"),  # Blue to red gradient
    name = "Mean Temperature (°C)"
  ) +
  theme_minimal() +
  labs(
    subtitle = "Warmer colors indicate higher temperatures",
    x = "Longitude",
    y = "Latitude"
  ) +
  theme(legend.position = "right")

@@

@fig-latitude-3 presents a geographic distribution of mean temperatures across Japan, with warmer colors indicating higher temperatures. This visualization highlights the spatial temperature variability across the country, where northern regions tend to have higher average temperatures compared to southern regions. The color gradient helps to illustrate how temperature conditions vary as a function of both latitude and longitude.

In summary, latitude has a significant influence on temperature, which directly impacts the timing of cherry blossom blooms. The relationship between latitude and temperature is well-captured by Figures 4, 5, and 6, which collectively demonstrate that regions at higher latitudes tend to experience higher average temperatures, contributing to earlier bloom periods. These insights are crucial for understanding the geographic factors that affect sakura florescence and for improving the accuracy of predictive models.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-flowerday-1
#| fig-cap: "Monthly Distribution of Flower Date"

#### Plot Monthly Distribution of Flower Date ####

@@

# Plot the monthly distribution
flower_month_plot <- ggplot(flower_month_distribution, aes(x = month, y = n)) +
  geom_bar(stat = "identity", fill = "steelblue", alpha = 0.8) +  # Use steelblue for the bars
  labs(
    x = "Month",
    y = "Count"
  ) +
  theme_minimal()

@@

@fig-flowerday-1 shows the monthly distribution of flower dates, with the majority of cherry blossoms blooming in March and April. This aligns with the typical cherry blossom season in Japan, which occurs in early spring. There are fewer occurrences of blooms in January, February, and May, which indicates that bloom timings outside of this window are uncommon, reflecting the strong seasonal pattern of sakura flowering.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-flowerday-2
#| fig-cap: "Flower Date Distribution by Month and Day"

#### Plot Distribution of Flower Dates by Month and Day ####

@@

# Plot the line graph
flower_date_line_plot <- ggplot(flower_date_summary, aes(x = day, y = count, color = month, group = month)) +
  geom_line(size = 1) +  # Draw smooth lines for each month
  scale_color_manual(values = color_palette) +  # Use a color palette for all months
  labs(
    x = "Day of the Month",
    y = "Count",
    color = "Month"
  ) +
  theme_minimal() +
  theme(
    legend.position = "right"
  )

@@

@fig-flowerday-2 presents a more detailed view of the flowering dates by month and day. The peak bloom periods are concentrated towards the end of March and throughout April, with the highest counts occurring in late April. This detailed distribution highlights the specific bloom dates, emphasizing how the bulk of flowering happens within a narrow time frame in early spring, largely driven by favorable temperature conditions.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-flowerday-3
#| fig-cap: "Temperature Distribution by Date"

#### Plot Distribution of Temperature by Date ####

@@

# Create the plot
temperature_plot <- ggplot(temperature_distribution, aes(x = day_of_year, y = mean_temp_month)) +
  geom_point(alpha = 0.5, color = "steelblue") +  # Scatter plot of temperature
  geom_smooth(method = "loess", color = "darkorange", size = 1, se = FALSE) +  # Smoothed line for trend
  labs(
    x = "Day of the Year",
    y = "Temperature (°C)"
  ) +
  scale_x_continuous(
    breaks = c(1, 32, 60, 91, 121, 152),  # Manually specify breaks for Jan, Feb, Mar, Apr, May
    labels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun")  # Correct labels
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )

@@

@fig-flowerday-3 shows the relationship between day of the year (DOY) for blooming and temperature. The trend line suggests a potential linear relationship, where later dates are associated with higher temperatures. This trend indicates that as the year progresses, temperatures rise, which influences the timing of cherry blossom blooms. The scatter plot further emphasizes the variation in temperatures experienced during different bloom periods, illustrating how the blooming date affects the observed temperature.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-flowerday-4
#| fig-cap: "Average Flowering Dates Across Japan"

#### Load and Prepare Data ####
# Calculate mean flower_doy for each location
sakura_summary <- sakura_modern_cleaned %>%
  group_by(latitude, longitude) %>%
  summarise(mean_flower_doy = mean(flower_doy, na.rm = TRUE)) %>%
  ungroup()

@@

#### Create the Map ####
gis_plot <- ggplot(data = japan_map) +
  geom_sf(fill = "white", color = "black") +  # Base map of Japan
  geom_point(
    data = sakura_summary,
    aes(x = longitude, y = latitude, color = mean_flower_doy),
    size = 3, alpha = 0.7
  ) +
  scale_color_viridis_c(
    option = "D",  # Viridis color scale for better visualization
    name = "Mean Flower DOY"
  ) +
  theme_minimal() +
  labs(
    subtitle = "Darker points indicate later flowering dates",
    x = "Longitude",
    y = "Latitude"
  ) +
  theme(legend.position = "right")

# Display the plot
print(gis_plot)
```

@fig-flowerday-4 provides a geographic overview of average flowering dates across Japan. The color gradient represents the mean flowering DOY, with darker points indicating later flowering dates. This map illustrates how flowering dates vary geographically, with earlier blooms occurring in warmer, southern regions and later blooms in cooler, northern regions. This geographic variation in bloom dates underscores the influence of temperature gradients across Japan.

In summary, the timing of cherry blossom blooms significantly affects temperature patterns. The majority of cherry blossoms bloom in March and April, which in turn correlates with observed temperature trends. Geographic variation also plays a significant role, with southern regions experiencing earlier blooms compared to northern regions. These insights are essential for understanding the temporal dynamics of sakura florescence and for enhancing the accuracy of predictive models that aim to understand temperature dynamics under varying bloom conditions. These insights are essential for understanding the temporal dynamics of sakura florescence and for enhancing the accuracy of predictive models that aim to forecast bloom timing under varying climatic conditions.

## Excluded Variables

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-year
#| fig-cap: "Temperature Trend Over Years"

#### Prepare Data ####
# sakura_historical_cleaned is already loaded
line_data <- sakura_historical_cleaned %>%
  filter(!is.na(temp), !is.na(year))  # Ensure no missing values

@@

#### Create Line Plot ####
line_plot <- ggplot(line_data, aes(x = year, y = temp)) +
  geom_line(color = "steelblue", size = 1) +  # Line graph with color and size
  geom_hline(
    yintercept = mean_temp, 
    color = "darkorange", 
    linetype = "dashed", 
    size = 1
  ) +  # Add horizontal dashed line for reference
  labs(
    x = "Year",
    y = "Temperature (°C)"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12)
  )

@@

@fig-year depicts the temperature trend over several centuries, highlighting the distribution of temperatures across different years. The orange dashed line represents the average temperature, providing a baseline for comparison. The plot shows considerable variation in temperatures from year to year, with no consistent linear trend. This lack of a clear relationship between temperature and year suggests that, over the long term, temperature fluctuations have been influenced by a complex interplay of factors beyond a simple time progression.

While there are periods of both high and low temperature variability, the data does not support a strong linear trend correlating temperature with time. This finding emphasizes that year-to-year temperature changes are not solely driven by temporal progression, but rather are subject to regional and potentially global climatic influences. Understanding these temperature trends is crucial for predicting future cherry blossom bloom timings, as temperature is a key determinant in bloom dynamics.

@@

@fig-longitude-1 shows the distribution of longitudes for the locations included in the dataset. The majority of the observations are concentrated between 135°E and 141°E, representing regions across central and eastern Japan. This distribution highlights the geographic focus of our study, which includes areas where cherry blossoms are commonly observed and where temperature data is readily available.

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-longitude-2
#| fig-cap: "Temperature VS Longitude"
